Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-10-11 reply_to_referee.tex

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{/images/fig_H-tau_fold.pdf}
\caption{Conformal transformation from the slit to cylinder.}
\label{fig:H-tau_fold}
\end{figure}

\reply{
We thank the referee for pointing out this sign error, in fact we used the $w \rightarrow \xi \rightarrow z$ order in the calculation as opposed to the $z \rightarrow \xi \rightarrow w$ order of the conformal transformation in the figure. We have fixed them.

Nevertheless we hold our opinion of using these two corrections to account for the missing $\frac{1}{12}\beta$. Let us reiterate our arguments.

The first correction comes from mapping the slit diagram to the annulus (in Fig. 6).  Before doing this conformal transformation, the short distance regulator is small on the $z$ plane. Hence the contribution of the free energy coming from introducing the two blue lines are small. However, after the transformation, we implicitly choose another regulator which is small on the $\xi$ plane. But by the change of this short distance cutoff, the $\xi$ plane erroneously contribute a $- \frac{c}{6} \ln \frac{r_2}{r_1}$ term from the outer surface. The compensation $+\frac{c}{6} \ln \frac{r_2}{r_1} = \frac{c}{6}\beta$ is the correction we are talking about.

@@

The is the lesson we learned from the Cardy-Peschel paper, where there are two explicit examples of computing the free energies of a corner and a cone. Both objects should be regarded as infinitely extended without boundaries at certain radii. The authors computed the correct results by conformally mapping the geometry to whole plane (or upper half plane) and contrasted with the calculation of the truncated corner and cone with both short and long distance regulators. They found that the discrepancies of the truncated cone and corner w.r.t. to the correct results come from the outer boundary contribution. By subtracting this otherwise nonexistent contribution using their proposed geodesic curvature formula, they are able to recover the correct result. We believe that the mapping from the $z$ to $\xi$ plane result in the same situation here.

We also change Fig 5, where in the left panel there is no vertical line IR regulator. So after doing the $\exp$ conformal transformation, the center diagram should be the upper half plane minus the small circle around $\xi = 1$. This is also an extended object, much the same way as the cone and corner in the Cardy-Peschel paper. To evaluate this extended diagram, we manually add another big semi-circle centered at $\xi = 1$ with radius $R_{\xi } \gg 1$. This will introduce a $-\frac{c}{6} \beta $ term that should not be there.

Then we move on to the $\xi$ to $w$ plane transformation. The staircase geometry Hamiltonian and the plane Hamiltonian is differed by the Schwartzian term in the transformation rule of the stress tensor, which gives $-\frac{c}{12} \beta $ correction. By gathering the two terms, we do get the desired $\frac{c}{12}\beta$ correction.

The content of this reply is supplemented in App. C. We request the referee to reconsider the presented arguments.
}

@@

(2) I also find the whole presentation of the mapping unsatisfactory. In part, this has to with the fact that no lengths are indicated in the figures.

For the fidelity, one maps in Fig. 5 the initial strip to an annulus with inner and outer radii determined by the length of the strip which goes to infinity. Then one moves the point, where the boundary condition changes, to the origin, which means that, in the strip, it is moved to the far left and disappears there. I cannot see, how the calculation then proceeds. In [25], a different conformal map was used.

\reply{
We have added more descriptions in the text around Fig.5 and Fig.6 about the conformal mappings used there. One major change is Fig 5. We do not impose IR regulator(previously a vertical line at $x = W$)  on the left panel of the slit diagram, but do add the small semi-circle. After doing the conformal mapping to the center diagram, we end up with a truncated corner centered at $z = 1$. To evaluate this diagram, we add another semi-circle centered at $z = 1$ with radius $R$. This should avoid the problem the referee was worried about.

(We add the semi-circle manually in the center of Fig. 5, which is incidentally in close analogy to the computation of the truncated cone and corner in the Cardy-Peschel paper. So to get the correct result, we should subtract its contribution to the free energy, which is exactly what we do in App. C.)

The annulus diagrams in both Fig. 5 and Fig. 6 are not strictly concentric to higher order corrections of $\frac{\epsilon}{L}, \frac{\epsilon}{\tau}$. To resolve this problem, (which the referee maybe worried about), we notice the following fact
\begin{itemize}
\item the conformal mapping from the non-concentric circles to the cylinder diagram exists: this can be done by first mapping the non-concentric circles to concentric circles and then use the $\ln z$ map. 
\item the resulting width of the cylinder only depend on the cross ratio of the intersection points of the two circles w.r.t. the real axis.  \rev{still don't get why the map is non-conformal}
\end{itemize}
since the conformal mapping preserve the cross ratio, we can calculate the width of the cylinder in terms of the cross ratio in the non-concentric circles. The calculation we did use the first order approximation of the cross ratio, but is enough to get the leading order of the width of the cylinder correct. The higher order corrections are of order $\frac{\epsilon}{L}$ and $\frac{\epsilon}{\tau}$, which should not affect the power law scalings of the fidelity and echo.

@@

This line of argument is also included in the main text below Fig. 6. 
}

For the Loschmidt echo, the starting point is again a strip of width L, as shown in Fig. 4. However, in the left part of Fig. 6 this width no longer appears. There is only a small remark in the text that $L \gg \tau$. But L is of significance, for finite L the ratio t/L enters, and in Ref. [25] this case could actually be treated.

\reply{We declared in the text (above Fig. 4) that we will take $L \gg \tau$ in all the echo computation. This keeps the problem with only one length scale.

  We are aware that such geometry with both finite $t$ and $L$ can be mapped to the upper half plane by the Schwarz-Christoffel mappings, as demonstrated in Ref.[25]. But the conformal interface, the dashed line, will be inside the upper half plane and we don't know how to calculate its OPE with the stress tensor. So in this paper, we only aim to understand the leading order behavior and its relation to the transmission coefficient. }

@@

\reply{We take this identification because the boundary state computation is easier.

In fact, since the distance between the blue lines ($\sim \ln L , \ln \tau$) on the $w$ plane in Fig.6 is much larger than the distance between the two dashed lines, one can view rotate this cylinder diagram and consider an evolution between the blue lines. This is the point of view taken by our alternative approach (an $S$ modular transformation to the figure in the boundary state calculation), the leading term of free energy is then the groundstate energy of the Hamiltonian given the boundary conditions on the dashed line, multiply by $\beta$, see Eq.(B8).

If one impose different boundary conditions on the blue lines, the free energy then is not 
\begin{equation}
F = - \ln \text{tr}( e^{ - \beta H_{ab} } ) =  \beta  E_c
\end{equation}
but (for large $\beta$ as is the case here)
\begin{equation}
\begin{aligned}
F &= - \ln \langle \text{blue boundary state 1} | e^{ - \beta H_{ab}} | \text{blue boundary state 2} \rangle \\
&= \beta  E_c - \ln \langle \text{blue boundary state 1} | \text{ground state} \rangle \\
 &\quad - \ln \langle \text{blue boundary state 2} |\text{ ground state }\rangle                                                                                 
\end{aligned}
\end{equation}
where the additional terms can be viewed as Affleck-Ludwig boundary entropy that is subleading (independent of $\beta$) in the free energy.

As far as the leading order (in beta) is concerned, the boundary conditions imposed on the blue line should not matter. We therefore take the simplest periodic boundary condition for the ease of computation.}

@@

(3) The calculation of the vacuum energy in equ.(E6) is not quite clear. Since the original expression diverges, a word about regularization would be in order. In the conversion of the sums into zeta functions (what does the index H mean ?) it seems to me that the n=0 terms are not handled correctly. The second function must be zeta(-1,-x). One could also imagine just giving a reference.

\reply{
A clarification is indeed necessary. We here use the Hurwitz zeta function regularization and so H stands for Hurwitz.

The final results, after a careful check is correct, however, the $x^{-s}$ term should be $-(-x)^{-s}$ if the $n = 0$ term is handled properly. Thanks for pointing this out!}

@@

But it is totally our fault not to check the number of references before submission. We have fixed it in this submission. }

(8) At no point could I see a remark on the analytical continuation from imaginary to real time. Instead, the notation changes back and forth between t and tau.

\reply{This point should be clarified in the introduction of the path-integral formalism(Sec. III. A.). All the path-integral spacetime diagrams are in the imaginary time. We only do analytic continuation to the final results of the imaginary time diagram.

We talk about the analytic continuation procedure between Eq.(16) and Fig.4 and demonstrate in Eq. (17). When referring to the imaginary path integral diagram, we use $\tau$ because that's the scale on Fig. 5 and Fig. 6. When representing the final result for Loschmidt echo, we do analytic continuation as Eq. (17). }

@@

4) After Eq. (17) it is stated that the boundary condition "c" is neglected. Isn't it taken to be "a" instead?

\reply{This statement is incorrect. It is taken to be a and changing it will influence the result even in the large L limit. So we did noÄôt neglect cÄ but taking it to be aÄô. We also take a simpler notation for this case after Eq. (17) }

5) Now we come to the main result of the paper, Eq. (23), that will yield all the exponents which will then be numerically verified. Despite this equation being the main results, its derivation is hidden away in an appendix. In fact all the calculations in this paper are demoted to be part of one of the numerous Appendix sections. I believe, that at least the main result should be given some space in the main text. I don't think this would compromise readability or accessibility of the results, in fact it think it would improve on it.

\reply{The derivation of Eq.(23) is contained in the original App. F, which is mainly the evaluation of partition function using a determinant identity with no physical arguments.

In order to improve readability, we first setup the calculation in the main text by explicitly spelling out the boundary states and the Hamiltonian in terms of the bosonic operators. We end up with an vacuum amplitude with three exponential of bilinears of bosonic operators in between. Such an expression can be evaluated using the determinant identity in the appendix. And we defer the detailed technical calculation in App. A.

In fact, we have rearranged the orders of the appendices for better accessibility.

### 2017-10-11 analy_eval.tex
[referee] 2nd round pass

\rev{Tian ci: Proofread this part for the conformal map}

For the fidelity case, the regulators as well as the conformal mappings are depicted in Fig.~\ref{fig:fidel-map}. 
\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{fig_fidel-map.pdf}
\caption{Mapping from a strip to the upper half plane $\xi  = \exp( \frac{\pi z}{L} ) $. The two black dots represent possible locations of boundary condition changing (bcc) operators. The dot inside the blue semi-circle is at coordinate $\xi = 1$, which is the image of the point connecting $a$ and $b$ boundaries. The other dot is at $\xi = 0$ and corresponds to the connection between $a$ and $c$ boundaries at $- \infty$. To evaluate the diagram, we add the outer blue semi-circle centered at $\xi = 1$ to be the IR cut-off and map it to the cylinder with $w = \ln(\xi - 1)$}
\label{fig:fidel-map}
\end{figure}
We add a small blue semi-circle to the folded strip in Fig.~\ref{fig:fidel} as the UV regulator and map it to the upper half plane using $\xi  = \exp( \frac{\pi z}{L} )$. Then both of $\xi = 0$ and $1$ can host bcc operators. We assume $a = c$ such that there is only one bcc operator on the real axis enclosed by the blue semi-circle at $\xi = 1$. In order to evaluate this diagram, we add another semi-circle centered at $\xi = 1$ with radius $R_{\xi}$ (this will introduce a correction as explained in App.~\ref{app:F_correction}), and map it to the cylinder diagram on the right by $w = \ln ( \xi- 1)$. Finally the cylinder diagram can be viewed as path integral amplitude between the boundary state $b$ and $a$
\begin{equation}
Z_{ab} = \langle a | e^{-\pi H } |b \rangle.
\end{equation}

@@

In App.~\ref{app:lambda_12}, we performed the calculation of the general partition function $S_a( \theta_1 ) \rightarrow S_b( \theta_2)$ and its free energy to the leading order of cylinder width $\beta$. A na\"ive application of the result however will lead to an apparent contradiction. One notable example is that when $a = b  = {\rm P}$, the free energy given by App.~\ref{app:lambda_12} is $- \frac{1}{12}\beta$, which should actually be {\it zero} because this is the (regularized) free energy on a plane without any interface. Physically this corresponds to the situation that the boundary condition does not change after joining the two chains. Hence the Loschmidt echo will stay at $1$ and the free energy is $0$. This motivates a shift to the free energy
\begin{equation}
\mathcal{F} = - \ln Z_{ab} ( \beta ) + \frac{1}{12} \beta ,
\end{equation}
where $\frac{1}{12}\beta$ is the value of $ \ln Z_{ab} ( \beta )$ when $a = b = {\rm P}$. A more careful inspection in App.~\ref{app:F_correction} shows the origin of the shift: part of it comes from the outer semi-circles in the middle panel of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}, and part comes from the non-homogeneous term in the conformation transformation of the stress tensor from annulus to cylinder.

>>>>

For the fidelity case, the regulators as well as the conformal mappings are depicted in Fig.~\ref{fig:fidel-map}. 
\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{fig_fidel-map.pdf}
\caption{Mapping from a strip to the upper half plane $\xi  = \exp( \frac{\pi z}{L} ) $. The two black dots represent possible locations of boundary condition changing (bcc) operators. The dot inside the blue semi-circle is at coordinate $\xi = 1$, which is the image of the point connecting $a$ and $b$ boundaries. The other dot is at $\xi = 0$ and corresponds to the connection between $a$ and $c$ boundaries at $- \infty$. To evaluate the diagram, we add the outer blue semi-circle centered at $\xi = 1$ to be the IR cut-off and map it to the cylinder with $w = \ln(\xi - 1)$}
\label{fig:fidel-map}
\end{figure}
We add a small blue semi-circle to the folded strip in Fig.~\ref{fig:fidel} as the UV regulator and map it to the upper half plane using $\xi  = \exp( \frac{\pi z}{L} )$. Then both $\xi = 0$ and $1$ can host bcc operators. We assume $a = c$ such that there is only one bcc operator on the real axis enclosed by the blue semi-circle around $\xi = 1$. In order to evaluate this diagram, we add another semi-circle centered around $\xi = 1$ with radius $R_{\xi}$ (this will introduce a correction as explained in App.~\ref{app:F_correction}), and map it to the cylinder diagram on the right by $w = \ln ( \xi- 1)$. Finally the cylinder diagram can be viewed as path integral amplitude between the boundary state $b$ and $a$
\begin{equation}
\label{eq:partition_fun}
Z_{ab} = \langle a | e^{-\pi H } |b \rangle.
\end{equation}

@@

The actual boundary conditions on the blue lines -- the regulators in Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold} are not important in the leading order. Taking Fig.~\ref{fig:H-tau_fold} for example, we can alternatively view the right panel as the amplitude between the two blue boundary states by a Hamiltonian with boundary condition $a$ and $b$
\begin{equation}
Z_{ab} =  \langle 1 | e^{ - \beta H_{ab}} | 2 \rangle  .
\end{equation}
Since $\beta$ --the width of the cylinder is large in this problem, we expect that the imaginary time evolution to project out only the groundstate $|0_{ab}\rangle $. Hence the free energy
\begin{equation}
\begin{aligned}
F &=  - \ln Z_{ab}  \sim - \ln \langle 1 |0_{ab} \rangle \langle   0_{ab}  |e^{ - \beta H_{ab}}|0_{ab} \rangle \langle 0_{ab} | 2 \rangle \\
&= \beta  E_c - \ln \langle 1| 0_{ab} \rangle  - \ln \langle 0_{ab}  |2 \rangle,
\end{aligned}
\end{equation}
where $E_c$ is the groundstate energy of $H_{ab}$. We see that different choice of the boundary conditions only change the term independent of $\beta$. Thus in the leading order we can choose any boundary condition. The one we pick is the simplest one: the periodic boundary condition that identifies the two blue lines.

Here we set up the partition function calculation of the general process $S_a( \theta_1 ) \rightarrow S_b( \theta_2)$ and leave the technical details to App.~\ref{app:lambda_12}. We define a set of bosonic operators related to the $a^i_n$s in Eq.~\eqref{eq:di_mode_expansion} through
\begin{equation}
\begin{aligned}
b^i_n &= \frac{a^i_n}{\sqrt{n}} \quad (b^i_n)^{\dagger} &= \frac{a^i_{-n}}{\sqrt{n}} \\
\bar{b}^i_n &= \frac{\bar{a}^i_n}{\sqrt{n}} \quad (\bar{b}^i_n)^{\dagger} &= \frac{\bar{a}^i_{-n}}{\sqrt{n}} \\
\end{aligned}
\end{equation}
for $n > 0 , i = 1, 2$, and group them compactly with the vector notation
\begin{equation}
\begin{aligned}
\vec{b}_i &= ( b^i_1, b^i_2, \cdots )^T, \quad \vec{\bar{b}}_i = ( \bar{b}^i_1, \bar{b}^i_2, \cdots )^T\\
\vec{b}^\dagger_i &= ( (b^i_1)^\dagger, (b^i_2)^\dagger, \cdots )^T, \quad\vec{\bar{b}}^{\dagger}_i = ( (\bar{b}^i_1)^\dagger, (\bar{b}^i_2)^\dagger, \cdots )^T .
\end{aligned}
\end{equation}
The boundary state in Eq.~\eqref{eq:bd_state} is then 
\begin{equation}
\exp\Big\{  (\vec{b}_1^{\dagger} \vec{b}_2^{\dagger} ) R_a( \theta )   
\begin{pmatrix}
  \vec{\bar{b}}_1^{\dagger}\\
  \vec{\bar{b}}_2^{\dagger}
\end{pmatrix}\Big\}  |0  \rangle ,
\end{equation}
where $R_a( \theta ) = -S_a \times \mathbb{I}$. Using even a lazier notation $\vec{b} = ( \vec{b}_1, \vec{b}_2 )$, we have
\begin{equation}
|a \rangle = \exp\Big\{  \vec{b}^{\dagger} R_a( \theta )    \vec{\bar{b}}^{\dagger} \Big\} |0 \rangle .
\end{equation}

The Hamiltonian of the folding picture has the mode expansion in terms of the $b_n$ (with periodic boundary conditions)
\begin{equation}
\begin{aligned}
  H &= \frac{2\pi}{\beta} (L_0 + \bar{L}_0) =  \frac{4\pi}{\beta}  L_0 \\
  &= \frac{4\pi}{\beta}\sum_{n > 0, i=1,2 }  n (b^i_n)^{\dagger} b^i_n \\
  &=  \frac{1}{\pi}(\vec{b}_1^{\dagger} \vec{b}_2^{\dagger} ) (\mathbb{I}_2  \otimes M)
\begin{pmatrix}
  \vec{{b}_1}\\
  \vec{{b}_2}
\end{pmatrix}\\
 &= \frac{1}{\pi} \vec{b}^{\dagger}  (\mathbb{I}_2  \otimes M)  \vec{b} ,
\end{aligned}
\end{equation}
where $L_0+ \bar{L}_0$ are the dilation operator in CFT and we have used the condition $L_0 = \bar{L}_0$ when restricted to the space of the boundary states. The infinite dimensional matrix $M$ is
\begin{equation}
M =  \frac{4\pi^2}{\beta} \text{diag}( 1, 2, \cdots ).
\end{equation}
The partition function is
\begin{equation}
\label{eq:Zab-bd}
\begin{aligned}
Z_{ab} =& \langle b | e^{-\pi H} | a \rangle \\
=& \langle 0 | \exp\Big\{  \vec{b} R_b( \theta )    \vec{\bar{b}} \Big\}  \exp\Big\{ -\vec{b}^{\dagger}  (\mathbb{I}_2  \otimes M)  \vec{b} \Big\} \\
&\exp\Big\{  \vec{b}^{\dagger} R_a( \theta )    \vec{\bar{b}}^{\dagger} \Big\} | 0\rangle .
\end{aligned}
\end{equation}

In App.~\ref{app:lambda_12}, we obtained the leading order term in the free energy associated with Eq.~\eqref{eq:Zab-bd}. A na\"ive application of the result however will lead to an apparent contradiction. One notable example is that when $a = b  = {\rm P}$, the free energy given by App.~\ref{app:lambda_12} is $- \frac{1}{12}\beta$, which should actually be {\it zero} because this is the (regularized) free energy on a plane without any interface. Physically this corresponds to the situation that the boundary condition does not change after joining the two chains. Hence the Loschmidt echo will stay at $1$ and the free energy is $0$. This motivates a shift to the free energy
\begin{equation}
\mathcal{F} = - \ln Z_{ab} ( \beta ) + \frac{1}{12} \beta ,
\end{equation}
where $\frac{1}{12}\beta$ is the value of $ \ln Z_{ab} ( \beta )$ when $a = b = {\rm P}$. A more careful inspection in App.~\ref{app:F_correction} shows the origin of the shift: part of it comes from the outer semi-circles in the middle panel of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}, and part comes from the non-homogeneous term in the conformation transformation of the stress tensor from annulus to cylinder.

### 2017-10-11 num_result.tex
[referee] 2nd round pass

Next, we analyze the more interesting $\theta$ dependent process ${\rm DN} \rightarrow \lambda$
%in Eq.~\eqref{eq:DNDN}
%\begin{equation}
%  \text{DN}+\text{DN}\rightarrow\lambda+\text{DN},
%\end{equation}
in which the joining boundary condition is determined by $S_1(\theta)$. We worked with a system containing $35000$ sites. A direct calculation with the mass regulator do not perform very well in the small $\theta$ regime: the exponent is slightly larger than the theoretical prediction. We therefore turn to another regulator that shift the far end boundary condition DN to $S_1( \delta \theta )$ and consider the following process
\begin{eqnarray}\begin{aligned}
\label{eq:approx_DNDN}
S_1(0)+S_1(\delta\theta)\rightarrow S_1(\theta)+S_1(\delta\theta),
\end{aligned}\end{eqnarray}
\rev{ where we have used the full notation as in Eq.~\eqref{eq:Full_notation_rand()}. }
Since ${\rm DN} = S_1 (0 )$, taking smaller and smaller $\delta \theta$ should correspond to the original process. This ``shift" regulator works very well for the fidelity calculation, where $\delta \theta = 0.001 \pi$, while moderately good for the Loschmidt echo, where $\delta \theta = 0.003\pi$, see Fig.~\ref{fig:DDNN}. The inset shows the $\theta$-dependence of power law decay, and the corresponding exponents follows the quadratic relation as predicted in Eq.~\eqref{eq:result_DNDN}. %We leave further discussion of introducing $\delta\theta$ in Sec.~\ref{sec:disc}.

@@

Finally, we also provide the data for the process
\begin{equation}
\label{eq:DNP_rand()}
{\rm DN} + {\rm P} \rightarrow \lambda  + {\rm P},
\end{equation}
to evaluate the influence of the boundary condition $c$. It {\rm does} influence the scaling dimension, which is not captured by our analytic calculation. We note that the exponent still follows the quadratic relation with a deficit of $\frac{1}{8}$ at large value of $\theta$. The deficit approaches zero at $\theta=0$ where the setups are the same before and after quench.
\begin{figure}[htb]
\centering
\includegraphics[width=1\columnwidth]{PDN_fit.pdf}
\caption{The decay exponent of Loschmidt echo for the process {\color{red}in Eq.~\eqref{eq:DNP_rand()}.} The boundary condition $c$, which is now different from $a$, changes the scaling completely from the analytic quadratic curve. The deficit to the analytic value is roughly $\frac{1}{8}$ for $\theta > \frac{\pi}{4}$, It becomes smaller and approaches zero for small $\theta$. }
\label{fig:PDN_fit}
\end{figure}

>>>>

Next, we analyze the more interesting $\theta$ dependent process ${\rm DN} \rightarrow \lambda$
%in Eq.~\eqref{eq:DNDN}
%\begin{equation}
%  \text{DN}+\text{DN}\rightarrow\lambda+\text{DN},
%\end{equation}
in which the joining boundary condition is determined by $S_1(\theta)$. We worked with a system containing $35000$ sites. A direct calculation with the mass regulator do not perform very well in the small $\theta$ regime: the exponent is slightly larger than the theoretical prediction. We therefore turn to another regulator that shift the far end boundary condition DN to $S_1( \delta \theta )$ and consider the following process
\begin{eqnarray}\begin{aligned}
\label{eq:approx_DNDN}
S_1(0)+S_1(\delta\theta)\rightarrow S_1(\theta)+S_1(\delta\theta),
\end{aligned}\end{eqnarray}
where we have used the full notation as in Eq.~\eqref{eq:Full_notation_rand()}. Since ${\rm DN} = S_1 (0 )$, taking smaller and smaller $\delta \theta$ should correspond to the original process. This ``shift" regulator works very well for the fidelity calculation, where $\delta \theta = 0.001 \pi$, while moderately good for the Loschmidt echo, where $\delta \theta = 0.003\pi$, see Fig.~\ref{fig:DDNN}. The inset shows the $\theta$-dependence of power law decay, and the corresponding exponents follows the quadratic relation as predicted in Eq.~\eqref{eq:result_DNDN}. %We leave further discussion of introducing $\delta\theta$ in Sec.~\ref{sec:disc}.

@@

Finally, we also provide the data for the process
\begin{equation}
\label{eq:DNP_rand()}
{\rm DN} + {\rm P} \rightarrow \lambda  + {\rm P},
\end{equation}
to evaluate the influence of the boundary condition $c$. It {\rm does} influence the scaling dimension, which is not captured by our analytic calculation. We note that the exponent still follows the quadratic relation with a deficit of $\frac{1}{8}$ at large value of $\theta$. The deficit approaches zero at $\theta=0$ where the setups are the same before and after quench.
\begin{figure}[htb]
\centering
\includegraphics[width=1\columnwidth]{PDN_fit.pdf}
\caption{The decay exponent of Loschmidt echo for the process in Eq.~\eqref{eq:DNP_rand()}. The boundary condition $c$, which is now different from $a$, changes the scaling completely from the analytic quadratic curve. The deficit to the analytic value is roughly $\frac{1}{8}$ for $\theta > \frac{\pi}{4}$, It becomes smaller and approaches zero for small $\theta$. }
\label{fig:PDN_fit}
\end{figure}
